---
output:
  bookdown::gitbook:
    lib_dir: "book_assets"
    includes:
      in_header: google_analytics.html
  html_document: default
  pdf_document: default
---
# Working with data 使用数据 {#working-with-data}

```{r echo=FALSE}
library(tidyverse)
library(cowplot)
```

## What are data? 什么是数据？

The first important point about data is that data *are* -- meaning that the word "data" is plural (though some people disagree with me on this).  You might also wonder how to pronounce "data" -- I say "day-tah", but I know many people who say "dah-tah", and I have been able to remain friends with them in spite of this. Now, if I heard them say "the data is" then that would be a bigger issue...

关于数据的第一个重要观点是，“data”是一个复数词（尽管有些人不同意我的看法）。也许，你还好奇“data”如何发音。我将之读作“day-tah”，但我也知道许多人将之读作“dah-tah”。尽管如此，我还是能和他们保持朋友关系。现在，当我听到他们将“data”作为单数使用，那么那将是一个更大的议题。

### Qualitative data 定性数据
Data are composed of *variables*, where a variable reflects a unique measurement or quantity.  Some variables are *qualitative*, meaning that they describe a quality rather than a numeric quantity.  For example, in my stats course I generally give an introductory survey, both to obtain data to use in class and to learn more about the students. One of the questions that I ask is "What is your favorite food?", to which some of the answers have been: blueberries, chocolate, tamales, pasta, pizza, and mango.  Those data are not intrinsically numerical; we could assign numbers to each one (1=blueberries, 2=chocolate, etc), but we would just be using the numbers as labels rather than as real numbers.  This also constrains what we should do with those numbers; for example, it wouldn't make sense to compute the average of those numbers.  However, we will often code qualitative data using numbers in order to make them easier to work with, as you will see later.

数据由一系列反映了不同的测量或数量的变量（*variables*）组成。其中一些变量是定性的（*Qualitative*）的，即这些变量描述了一种性质而不是数量的多少。例如，我通常会在统计课程的导论课上做一个摸底调查，既是为了获取课堂上可用的数据，也是为了更好地了解我的学生。其中有一个问题是“你最喜欢的食物是什么？”，题目的选项包括蓝莓、巧克力、墨西哥玉米卷、意大利面、披萨和芒果，等等。这些数据本质上不是数量化的，我们没法将数字赋值给每一个选项（例如1=蓝莓，2=巧克力，以此类推），但是我们可以仅将数字用作标签而非真实的数字。这也同样约束了我们使用这些数字的方式。例如，比较这些数字的均值是没有意义的。但是正如你们将要看到的，我们经常将定性数据编码为数字，以便于我们使用数据。

### Quantitative data 定量数据
More commonly in statistics we will work with *quantitative* data, meaning data that are numerical.  For example, here Table \@ref(tab:WhyTakingClass) shows the results from another question that I ask in my introductory class, which is "Why are you taking this class?"

在统计，我们更经常处理可以被数量化的定量（*quantitative*）数据。例如，Table \ref(tab:WhyTakingClass) 展示了我的摸底调查的另一个问题“你为什么上这门课”的结果。

```{r WhyTakingClass,echo=FALSE}
# create table showing frequency of responses to question about why students
# are taking statistics class

classData=data.frame(why=c("It fulfills a degree plan requirement 符合学位计划的要求",
                           "It fulfills a General Education Breadth Requirement 满足General Education Breadth Requirement",
                           "It is not required but I am interested in the topic 出于兴趣",
                           "Other 其他"),
                     nResponses=c(105,32,11,4))

knitr::kable(
  classData, booktabs = TRUE,
  caption = 'Counts of the prevalence of different responses to the question "Why are you taking this class?" “为什么上这门课”的不同回答的普遍性',
  col.names=c('Why are you taking this class? 为什么上这门课',"Number of students 选择此项的学生数")
)
```

Note that the students' answers were qualitative, but we generated a quantitative summary of them by counting how many students gave each response.  

请注意学生的答案是定性的，但是我们根据选择不同回答的学生的数量生成了定量的总结。

#### Types of numbers 数的类型
There are several different types of numbers that we work with in statistics.  It's important to understand these differences, in part because statistical analysis languages (such as R) often distinguish between them.

在统计学中，有几种不同类型的数。理解他们的差异是重要的，原因之一在于统计分析语言（例如R）经常会区分这些类型的数。

**Binary numbers**. The simplest are binary numbers -- that is, zero or one.  We will often use binary numbers to represent whether something is true or false, or present or absent.  For example, I might ask 10 people if they have ever experienced a migraine headache, recording their answers as "Yes" or "No".  It's often useful to instead use *logical* values, which take the value of either ```TRUE``` or ```FALSE```.  This can be especially useful when we start using programming languages like R to analyze our data, since these languages already understand the concepts of TRUE and FALSE.  In fact, most programming languages treat truth values and binary numbers equivalently. The number 1 is equal to the logical value ```TRUE```, and the number zero is equal to the logical value ``FALSE``.

**Binary numbers**。最简单的数是Binary numbers，他们的取值只能是0或者1。我们经常将Binary numbers用于表示某事是真（true）还是假（false），是存在还是不存在。例如，我可以向10个人询问他们是否有偏头痛，并将他们的回答记录为“是”或“否”。使用逻辑值（*logical* value）来代替Binary numbers的做法非常常见，*logical*值只能是```TRUE```（真）或```FALSE```（假）。由于程序语言（例如R）普遍有TRUE和FALSE的概念，这在我们开始使用程序语言时将十分有帮助。事实上，绝大多数程序语言将二者视为等同。数字1等价于逻辑值的真（```TRUE```），而数字0等价于逻辑值的假（```FALSE```）。

**Integers**.  Integers are whole numbers with no fractional or decimal part. We most commonly encounter integers when we count things, but they also often occur in psychological measurement.  For example, in my introductory survey I administer a set of questions about attitudes towards statistics (such as "Statistics seems very mysterious to me."), on which the students respond with a number between 1 ("Disagree strongly") and 7 ("Agree strongly").  

**整数（Integers）**。整数是没有小数部分的数。整数是我们在计数时最常遇到的数，它们也同样出现在心理学测量中。例如，我在摸底调查中，提出了一组对统计学的态度的题器（如“统计学对我而言似乎很神秘”）。这些题器的答案被设置为1（表示“强烈不同意”）到7（表示“强烈同意”）之间的数字。

**Real numbers**.  Most commonly in statistics we work with real numbers, which have a fractional/decimal part.  For example, we might measure someone's weight, which can be measured to an arbitrary level of precision, from kilograms down to micrograms.

**实数（Real numbers）**。实数是我们在统计学中最常使用的数，它是带有小数部分的数。例如，我们可能会想要测量一个人的体重。而体重可以在从千克到微克的任意精度上被测量。

## Discrete versus continuous measurements 离散测量与连续测量

A *discrete* measurement is one that takes one of a finite set of particular values.  These could be qualitative values (for example, different breeds of dogs) or numerical values (for example, how many friends one has on Facebook).  Importantly, there is no middle ground between the measurements; it doesn't make sense to say that one has 33.7 friends.

离散（*discrete*）测量指在有限的一组特定的值中取一个。这些值可以是定性的取值（例如，不同品种的狗）或定量的数值（例如，一个人在Facebook上有多少个朋友）。重要的是，这些测量之间没有中间地带。说一个人有33.7个朋友是没有意义的。

A *continuous* measurement is one that is defined in terms of a real number. It could fall anywhere in a particular range of values, though usually our measurement tools will limit the precision with which we can measure it; for example, a floor scale might measure weight to the nearest kg, even though weight could in theory be measured with much more precision.

连续（*continuous*）测量是以实数定义的。值可以落在一个特定的数值范围内的任何地方，尽管测量的精度常常被测量工具所限制。例如，地磅测量的结果通常精确到千克，尽管理论上可以用更高的精度来测量质量。

It is comm on in statistics courses to go into more detail about different "scales" of measurement, which are discussed in more detail in the Appendix to this chapter.  The most important takeaway from this is that some kinds of statistics don't make sense on some kinds of data.  For example, imagine that we were to collect postal Zip Code data from a number of individuals. Those numbers are represented as integers, but they don't actually refer to a numeric scale; each zip code basically serves as a label for a different region. For this reason, it wouldn't make sense to talk about the average zip code, for example.  

在统计学课程中，对不同的测量“尺度”进行更详细的讨论是很有必要的，本章的附录对此进行了详细讨论。从中得到的最重要的启示是，某些种类的统计在某些种类的数据上是没有意义的。以邮政编码为例，尽管这些数字被表示为整数，但它们实际上并不是指一个数字尺度；邮政编码事实上是地区的标签。因此，在这个例子中，谈论平均邮政编码是没有意义的。

## What makes a good measurement? 什么才是好的测量方法？

In many fields such as psychology, the thing that we are measuring is not a physical feature, but instead is an unobservable theoretical concept, which we usually refer to as a *construct*.  For example, let's say that I want to test how well you understand the distinction between the different types of numbers described above.  I could give you a pop quiz that would ask you several questions about these concepts and count how many you got right.  This test might or might not be a good measurement of the construct of your actual knowledge -- for example, if I were to write the test in a confusing way or use language that you don't understand, then the test might suggest you don't understand the concepts when really you do. On the other hand, if I give a multiple choice test with very obvious wrong answers, then you might be able to perform well on the test even if you don't actually understand the material.  

在诸如心理学的许多领域中，我们要测量的事物并不是一个物理的特征，而是一个不可观测的理论概念（我们通常称之为“结构”（*construct*））。例如，我想测量你对上述不同类型的数的理解程度。我可以给你一个突击测试，考察几道关于这些概念的问题，然后计算回答正确的个数。这一测量可能是，也可能不是，对你实际知识结构的一个好的测量——如果题目很混乱、或者使用你不理解的语言，那么可能导致测试结果反映你不理解而事实上你是理解的结果。另一方面，如果我给出一个具有非常明显的错误答案的多选题测试，那么即便你实际上并不理解，也可能在测试中表现良好。

It is usually impossible to measure a construct without some amount of error.  In the example above, you might know the answer, but you might mis-read the question and get it wrong.  In other cases, there is error intrinsic to the thing being measured, such as when we measure how long it takes a person to respond on a simple reaction time test, which will vary from trial to trial for many reasons. We generally want our measurement error to be as low as possible, which we can achieve either by improving the quality of the measurement (for example, using a better time to measure reaction time), or by averaging over a larger number of indvidiual measurements.  

通常情况下，对结构的测量都是有误差的。在上面的例子中，你可能知道答案，但因为误读问题而回答错误。在其他情况下，被测量的事物本身就存在误差。例如，当我们测量一个人在简单的反应时间测试中需要多长时间做出反应时，由于各种各样的原因，不同的试验会有不同的结果。我们通常希望我们的测量误差越小越好，这可以通过提高测量的质量（例如，使用更好的计时器来测量反应时间），或者通过在更多的内部测量中取平均值来实现。 

Sometimes there is a standard against which other measurements can be tested, which we might refer to as a "gold standard" -- for example, measurement of sleep can be done using many different devices (such as devices that measure movement in bed), but they are generally considered inferior to the gold standard of polysomnography (which uses measurement of brain waves to quantify the amount of time a person spends in each stage of sleep).  Often the gold standard is more difficult or expensive to perform, and the cheaper method is used even though it might have greater error.

某些测量方法可以被用来测试其他测量方法，它们被称作“黄金标准”。例如，我们可以用许多不同的设备（如测量床上动作的设备）来测量睡眠，但它们通常被认为不如多导睡眠仪这一黄金标准（使用脑电波测量来量化一个人在每个睡眠阶段的时间）。通常情况下，黄金标准更难执行或更昂贵，更便宜的方法则会被使用，尽管可能有更大的误差。

When we think about what makes a good measurement, we usually distinguish two different aspects of a good measurement: it should be *reliable*, and it should be *valid*.

当我们思考什么是好的测量时，我们通常会在两个方面考量：测量应该是可靠的（*reliable*），同时也应该是有效的（*valid*）。

### Reliability 信度

Reliability refers to the consistency of our measurements.  One common form of reliability, known as "test-retest reliability", measures how well the measurements agree if the same measurement is performed twice.  For example, I might give you a questionnaire about your attitude towards statistics today, repeat this same questionnaire tomorrow, and compare your answers on the two days; we would hope that they would be very similar to one another, unless something happened in between the two tests that should have changed your view of statistics (like reading this book!).  

信度（reliability）即是测量的一致性。再测信度（test-retest reliability）是信度的一种常见形式，被用于衡量两次相同的测量的一致性。例如，我在今天让你填写一份关于对统计学的台独的问卷，然后在明天让你填写一份同样的问卷。我们希望你的两份问卷答案非常相似，除非在两次测量之间发生了一些可能改变你对统计学的看法的事情（比如阅读这本书！）。

Another way to assess reliability comes in cases where the data include subjective judgments.  For example, let's say that a researcher wants to determine whether a treatment changes how well an autistic child interacts with other children, which is measured by having experts watch the child and rate their interactions with the other children.  In this case we would like to make sure that the answers don't depend on the individual rater --- that is, we would like for there to be high *inter-rater reliability*.  This can be assessed by having more than one rater perform the rating, and then comparing their ratings to make sure that they agree well with one another.

在数据包含主观判断的情况下，我们可以使用另一种信度评估的方法。例如，假设研究者想要通过让专家观察自闭症儿童并对其与其他儿童的互动情况评分，以确定一种旨在改善自闭症儿童与其他儿童的互动情况的治疗方法是否有效。在这种情况下，我们希望确保答案不取决于个别评分者——即希望有较高的评分者间的信度（*inter-rater reliability*）。实现这一目标的方法可以是让一个以上的评分者进行评分，然后比较评分以确保彼此之间的一致性。

Reliability is important if we want to compare one measurement to another, because the relationship between two different variables can't be any stronger than the relationship between either of the variables and itself (i.e., its reliability).  This means that an unreliable measure can never have a strong statistical relationship with any other measure.  For this reason, researchers developing a new measurement (such as a new survey) will often go to great lengths to establish and improve its reliability.

当我们想要将一个测量与另一个测量进行比较时，信度是非常重要的，因为两个不同变量之间的关系不可能比其中任一变量与它本身的关系（即信度）更强。这意味着，一个缺乏信度的测量永远不可能与其他测量有着强统计相关。因此，研究者往往会在开发新测量方法（如一个新的调查）时，不遗余力地建立和提高其信度。

```{r ReliabilityValidity, echo=FALSE,fig.cap="A figure demonstrating the distinction between reliability and validity, using shots at a bullseye. Reliability refers to the consistency of location of shots, and validity refers to the accuracy of the shots with respect to the center of the bullseye. \n使用射击结果展示信度与效度地区别。信度是射击位置的一致性，而效度则是射击位置相对于靶心地准确性。",fig.width=6,fig.height=6,out.height='33%'}
# Figure inspired by https://commons.wikimedia.org/wiki/File:Reliability_and_validity.svg
# 图的灵感来自于 https://commons.wikimedia.org/wiki/File:Reliability_and_validity.svg

# from https://stackoverflow.com/questions/6862742/draw-a-circle-with-ggplot2
# 自 https://stackoverflow.com/questions/6862742/draw-a-circle-with-ggplot2

set.seed(12345)
gg_circle <- function(r, xc, yc, color="black", fill=NA, ...) {
    x <- xc + r*cos(seq(0, pi, length.out=100))
    ymax <- yc + r*sin(seq(0, pi, length.out=100))
    ymin <- yc + r*sin(seq(0, -pi, length.out=100))
    annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}


npoints <- 16
rel_mult <- 0.75
unrel_mult <- 2.5

plotDf <- tibble(
  X_RelVal = rnorm(npoints)*rel_mult,
  Y_RelVal = rnorm(npoints)*rel_mult,
  X_RelInval = rnorm(npoints)*rel_mult+2,
  Y_RelInval = rnorm(npoints)*rel_mult+2,
  X_UnrelInval = rnorm(npoints)*unrel_mult+2,
  Y_UnrelInval = rnorm(npoints)*unrel_mult+2,
  X_UnrelVal = rnorm(npoints)*unrel_mult,
  Y_UnrelVal = rnorm(npoints)*unrel_mult
)

pointsize <- 3
linesize=2
p1=ggplot(plotDf,aes(X_RelVal,Y_RelVal)) +
  gg_circle(r=4, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=3, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=2, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=1, xc=0.0, yc=0.0,size=linesize,color='red',fill='red') + 
  geom_point(size=pointsize) + 
  xlim(-10,10) + ylim(-10,10) + 
  theme_void()

p2=ggplot(plotDf,aes(X_UnrelVal,Y_UnrelVal)) +
  gg_circle(r=4, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=3, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=2, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=1, xc=0.0, yc=0.0,size=linesize,color='red',fill='red') +
  geom_point(size=pointsize) + 
  xlim(-10,10) + ylim(-10,10) + 
  theme_void() 

p3=ggplot(plotDf,aes(X_RelInval,Y_RelInval)) +
  gg_circle(r=4, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=3, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=2, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=1, xc=0.0, yc=0.0,size=linesize,color='red',fill='red') + 
  geom_point(size=pointsize) + 
  xlim(-10,10) + ylim(-10,10) + 
  theme_void() 

p4=ggplot(plotDf,aes(X_UnrelInval,Y_UnrelInval)) +
  gg_circle(r=4, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=3, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=2, xc=0.0, yc=0.0,size=linesize,color='red') + 
  gg_circle(r=1, xc=0.0, yc=0.0,size=linesize,color='red',fill='red') + 
  geom_point(size=pointsize) + 
  xlim(-10,10) + ylim(-10,10) + 
  theme_void() 

plot_grid(p1,p2,p3,p4,ncol=2,label_size=12,
          labels=c('A: Reliable and valid\n信效度俱佳',
                   'B: Unreliable but valid\n效度高但信度低',
                   'C: Reliable but invalid\n信度高而效度低',
                   'D: Unreliable and invalid\n信效度皆低'))


```

### Validity 效度

Reliability is important, but on its own it's not enough: After all, I could create a perfectly reliable measurement on a personality test by re-coding every answer using the same number, regardless of how the person actually answers.  We want our measurements to also be *valid* --- that is, we want to make sure that we are actually measuring the construct that we think we are measuring (Figure \@ref(fig:ReliabilityValidity)). There are many different types of validity that are commonly discussed; we will focus on three of them.

信度是重要的，但就测量的目的而言并不足够：毕竟，在人格测试中，我可以通过将答案重编码为相同的数字来创建一个完全一致的测量，而不管这个人实际上如何回答。我们希望我们的测量结果同时是有效的（*valid*）——即希望我们测量的结构确实是我们想要测量的（Figure \@ref(fig:ReliabilityValidity)）。效度有很多种不同的类型，我们将重点讨论其中的三种。

*Face validity*. Does the measurement make sense on its face?  If I were to tell you that I was going to measure a person's blood pressure by looking at the color of their tongue, you would probably think that this was not a valid measure on its face.  On the other hand, using a blood pressure cuff would have face validity.  This is usually a first reality check before we dive into more complicated aspects of validity.

表面效度（*Face validity*；译注：也称作内容效度、逻辑效度）。测量是否在表面上有意义？如果我想要通过观察舌头的颜色来测量血压，你可能会认为这不是一个表面上有效的测量。另一方面，使用血压计则具有表面效度。表面效度往往是在我们深入研究效度更复杂的其他方面之前的首次检查。

*Construct validity*.  Is the measurement related to other measurements in an appropriate way?  This is often subdivided into two aspects.  *Convergent validity* means that the measurement should be closely related to other measures that are thought to reflect the same construct. Let's say that I am interested in measuring how extroverted a person is using either a questionnaire or an interview.  Convergent validity would be demonstrated if both of these different measurements are closely related to one another.  On the other hand, measurements thought to reflect different constructs should be unrelated, known as *divergent validity*.  If my theory of personality says that extraversion and conscientiousness are two distinct constructs, then I should also see that my measurements of extraversion are *unrelated* to measurements of conscientiousness.  

结构效度（*Construct validity*）。测量是否以适当的方式与其他测量相关？结构效度通常被分为两个方面：聚合效度（*Convergent validity*；译注：也称作收敛效度）指测量结果与其他被认为能够反映同一结构的测量结果密切相关。例如，我对使用问卷调查或访谈来测量一个人的外向程度感兴趣。如果两种不同的测量结果高度相关，那么就可以证明测量具有聚合效度。另一方面，区别效度（*divergent validity*；译注：也称作分歧效度）指测量结果与反映其他结构的测量结果不相关。例如，我的人格理论认为外倾性（extraversion）和自觉性（conscientiousness）是两个不同的结构，那么我关于外倾性的测量结果应当与关于自觉性的测量结果不相关。

*Predictive validity*.  If our measurements are truly valid, then they should also be predictive of other outcomes.  For example, let's say that we think that the psychological trait of sensation seeking (the desire for new experiences) is related to risk taking in the real world.  To test for predictive validity of a measurement of sensation seeking, we would test how well scores on the test predict scores on a different survey that measures real-world risk taking. 

预测效度（*Predictive validity*）。如果我们的测量是真正有效的，那么它们也应该能够预测其他结果。例如，假设我们认为寻求感觉（对新体验的渴望）的心理特征与现实世界中的风险承担有关，那么我们可以测试对这一心理特征的测量得分能在多大程度上预测另一调查中的现实世界风险承担得分。

## Learning Objectives 学习目标

Having read this chapter, you should be able to:

通过阅读本章，你应当能够：

* Distinguish between different types of variables (quantitative/qualitative, binary/integer/real, discrete/continuous) and give examples of each of these kinds of variables
* 区分不同种类的变量（定性/定量，binary/整数/实数，离散/连续），并给出不同种类变量的例子；
* Distinguish between the concepts of reliability and validity and apply each concept to a particular dataset
区分信度和效度的概念，并将概念应用在具体的数据集中。


## Suggested readings 推荐阅读

- [*An Introduction to Psychometric Theory with Applications in R*](http://www.personality-project.org/r/book/) - A free online textbook on psychological measurement

## Appendix 附录

### Scales of measurement 测量尺度

All variables must take on at least two different possible values (otherwise they would be a *constant* rather than a variable), but different values of the variable can relate to each other in different ways, which we refer to as *scales of measurement*.  There are four ways in which the different values of a variable can differ.

所有的变量都必须有至少两个不同的可能取值（否则它就是一个常量（*constant*）而非变量），但是变量的不同取值可以以不同的方式相互联系，我们称之为“测量尺度”（*scales of measurement*）。一个变量的不同取值可以通过四种方式区分：

- *Identity*: Each value of the variable has a unique meaning.  
- 特征（*Identity*）：变量的每个取值都有独一无二的含义；
- *Magnitude*: The values of the variable reflect different magnitudes and have an ordered relationship to one another -- that is, some values are larger and some are smaller.
- 大小（*Magnitude*）：变量的取值反映了不同的大小，且具有有序关系——也就是说，有些值比较大，有些值比较小；
- *Equal intervals*: Units along the scale of measurement are equal to one another. This means, for example, that the difference between 1 and 2 would be equal in its magnitude to the difference between 19 and 20.
- 等距（*Equal intervals*）：沿着测量尺度的单位是彼此相等的。这意味着，1和2之间的差异在大小上等于19和20之间的差异；
- *Absolute zero*:  The scale has a true meaningful zero point. For example, for many measurements of physical quantities such as height or weight, this is the complete absence of the thing being measured.
- 绝对零点（*Absolute zero*）：测量尺度具有一个有实际意义的零点，例如在许多诸如身高、体重的物理量的测量，0代表着被测量事物的完全不存在。

There are four different scales of measurement that go along with these different ways that values of a variable can differ.

如下四种不同的测量尺度基于变量取值的不同区分方式：

*Nominal scale*.  A nominal variable satisfies the criterion of identity, such that each value of the variable represents something different, but the numbers simply serve as qualitative labels as discussed above.  For example, we might ask people for their political party affiliation, and then code those as numbers: 1 = "Republican", 2 = "Democrat", 3 = "Libertarian", and so on. However, the different numbers do not have any ordered relationship with one another.  

定类（*Nominal scale*）。定类变量满足特征的标准，变量的每个值都代表不同的事物，但数字只是前文所讨论的定性标签。例如，我们可能会询问人们的正当归属，然后将其编码为数字：1 = “共和党人”、2 = “民主党人”、3 = “自由主义者”，等等。然而，不同的数字之间并没有任何有序的关系。

*Ordinal scale*. An ordinal variable satisfies the criteria of identity and magnitude, such that the values can be ordered in terms of their magnitude.  For example, we might ask a person with chronic pain to complete a form every day assessing how bad their pain is, using a 1-7 numeric scale. Note that while the person is presumably feeling more pain on a day when they report a 6 versus a day when they report a 3, it wouldn't make sense to say that their pain is twice as bad on the former versus the latter day; the ordering gives us information about relative magnitude, but the differences between values are not necessarily equal in magnitude.

定序（*Ordinal scale*）。定序变量满足特征和大小的标准，变量的每个取值可以根据其大小排序。例如，我们可以要求患有慢性疼痛的人每天填写一份表格，用1-7的数字量表来评估他们的疼痛程度。请注意，虽然同一个患者在报告6分的日子相比在报告3分的日子里感到更痛，单说在前者时的疼痛是在后者时的疼痛的2倍是没有意义的；排序提供了关于相对大小的信息，但数值之间的差异并不一定是相等的。

*Interval scale*. An interval scale has all of the features of an ordinal scale, but in addition the intervals between units on the measurement scale can be treated as equal.  A standard example is physical temperature measured in Celsius or Fahrenheit; the physical difference between 10 and 20 degrees is the same as the physical difference between 90 and 100 degrees, but each scale can also take on negative values.

定距（*Interval scale*）。定居变量满足定序变量的特征，同时各单位之间的间隔是相等的。以摄氏度和华氏度测量的物理温度是定距变量的标准例子：10度与20度之间的物理差异与90度和100度之间的物理差异是相等的，同时变量也可以取负值。

*Ratio scale*. A ratio scale variable has all four of the features outlined above: identity, magnitude, equal intervals, and absolute zero.  The difference between a ratio scale variable and an interval scale variable is that the ratio scale variable has a true zero point.  Examples of ratio scale variables include physical height and weight, along with temperature measured in Kelvin.

定比（*Ratio scale*）。定比变量同时具备上述四个特征：特性、大小、等距和绝对零点。定比变量与定距变量之间的区别在于定比变量具有一个真正的零点。定比变量的实例包括身高、体重，以及以开尔文为单位的温度。

There are two important reasons that we must pay attention to the scale of measurement of a variable.  First, the scale determines what kind of mathematical operations we can apply to the data (see Table \@ref(tab:MeasurementTypes)).  A nominal variable can only be compared for equality; that is, do two observations on that variable have the same numeric value?  It would not make sense to apply other mathematical operations to a nominal variable, since they don't really function as numbers in a nominal variable, but rather as labels.  With ordinal variables, we can also test whether one value is greater or lesser than another, but we can't do any arithmetic.  Interval and ratio variables allow us to perform arithmetic; with interval variables we can only add or subtract values, whereas with ratio variables we can also multiply and divide values.  

出于两个重要的原因，我们必须注意变量的测量尺度。首先，尺度决定了我们可以对数据进行的数学运算（见Table \@ref(tab:MeasurementTypes)）。定类变量只能进行相等运算，即两个值是否相等。对定类变量应用其他数学运算是没有意义的，因为定类变量的取值并不真正起到数字的作用，而仅仅是标签。对于定序变量，我们可以测试一个数值是否大于或小于另一个数值，但我们不能做任何算数。定距变量和定比变量允许算术；定距变量只允许加减，而定比变量还允许乘除。

```{r echo=FALSE,MeasurementTypes}

measTypes=data.frame(equal=c('OK','OK','OK','OK'),
                     gtlt=c('','OK','OK','OK'),
                     addsub=c('','','OK','OK'),
                     multdiv=c('','','','OK'),
                     row.names=c('Nominal\n定类','Ordinal\n定序','Interval\n定距','Ratio\n定比'))
knitr::kable(
  measTypes, booktabs = TRUE,
  caption = 'Different scales of measurement admit different types of numeric operations\n不同测量尺度允许不同类型的数学运算',
  col.names=c("Equal/not equal\n相等/不等",">/<", "+/-", "Multiply/divide\n乘/除")
)


```

These constraints also imply that there are certain kinds of statistics that we can compute on each type of variable.  Statistics that simply involve counting of different values (such as the most common value, known as the *mode*), can be calculated on any of the variable types.  Other statistics are based on ordering or ranking of values (such as the *median*, which is the middle value when all of the values are ordered by their magnitude), and these require that the value at least be on an ordinal scale.  Finally, statistics that involve adding up values (such as the average, or *mean*), require that the variables be at least on an interval scale.  Having said that, we should note that it's quite common for researchers to compute the mean of variables that are only ordinal (such as responses on personality tests), but this can sometimes be problematic.  

这些约束条件同样意味着我们可以在不同类型的变量上计算不同种类的统计量。简单涉及不同取值的技术的统计量（如最常见的值，即“众数”（*mode*））可以在任何类型的变量上计算。其他基于数值的排序或排名的统计量（例如“中位数”（*median*），即所有数值按大小排序时的中间值）要求变量至少是定序变量。最后，涉及数值相加的统计量（例如平均数，或均值（“mean”））要求变量至少是定距变量。至此，我们应该注意，对研究人员而言，计算定序变量的平均值时很常见的（如人格测试的结果），但这有时会有问题。
